Soundness Proofs for Iterative Deepening

### 2015-11-20 pldi-16/proof/di.tex
clean up todos

The same as in the paper, we distinguish between data-race {\em candidates} and data-race {\em bugs}.
In this proof we are concerned solely with candidates, and judging whether they are true data races or false positives.
It is up to \quicksand, outside the scope of this proof, to decide whether true data races are benign or buggy.

>>>>

The same as in the paper, we distinguish between data-race {\em candidates} and data-race {\em bugs}.
In this proof we are concerned solely with candidates, and wheter they can be observed to race or are false positives.
It is up to the MC to decide whether true data races are benign or buggy.
